---
title: "Project6 Red Wine Analysis"
author: "Maria Dubyaga"
date: "January 6, 2019"
output: html_document
---
========================================================

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
install.packages("weatherData",repos = "http://cran.us.r-project.org")
options(repos="https://cran.rstudio.com" )
install.packages("ggplot2")
library(ggplot2)
library(gridExtra)
install.packages("plotly")
library(plotly)
install.packages('corrplot')
library(corrplot)
library(GGally)
library(scales)
library(memisc)
library(MASS)
library(car)
library(reshape)
library(plyr)
library(dplyr)
library(RColorBrewer)
library(pander)
library("Hmisc")
install.packages('xtable')
library(xtable)
#install.packages('tibble')
#library(tibble)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_the_Data}
# Load the Data
redWine <- read.csv('wineQualityReds.csv')

```

## The dataset description:
  This tidy data set contains 1,599 red wines with 11 variables on the chemical properties of the wine. At least 3 wine experts rated the quality of each wine, providing a rating between 0 (very bad) and 10 (very excellent).

## The question the analysis is answering
  Which chemical properties influence the quality of red wines?


# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE}
# to check the variables
names(redWine)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# to check types
str(redWine)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# to check how the dataset looks like
head(redWine)
```

### Variables limits and mean/median     
```{r echo=FALSE, message=FALSE, warning=FALSE}
sumWine <- summary(redWine)
sumWine
```

### Summarizing wine by Quality Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
#  Info : https://www3.nd.edu/~steve/computing_with_data/24_dplyr/dplyr.html
# need to group quality into groups to analyze it 
veryBad <- c(1,2)
bad <- c(3,4)
good <- c(5,6)
excellent <- c(7,8)
veryExcellent <- c(9,10)

redWine$QualityGroup <- with(redWine, ifelse(redWine$quality %in% veryBad, "Very Bad",
                              ifelse(redWine$quality %in% bad, "Bad",
                                     ifelse(redWine$quality %in% good, 'Good',
                                            ifelse(redWine$quality %in% excellent, 'Excellent', 'Very Excellent')))))


table(redWine$QualityGroup)
```
### Group Quality distribution

```{r echo=FALSE, message=FALSE, warning=FALSE, GroupQuality}

pQG <-ggplot(redWine, aes(x=QualityGroup)) +
  geom_bar(color ='black', fill = I('orange')) + xlab('Quality Group')

grid.arrange(pQG, ncol =2)
```

  
As we seen from the previuos summary we don't have wine with ranking 1,2 \
(which is supposed to be 'very bad' and 9,10 which is supposed to be 'very \
excellent').

I've groupped the rest into groups:
"Bad": ranking 3,4
"Good" ranking 5,6
"Excellent": ranking 7,8
As we see, the most of the samplses 85% falls into 'Good' wine category.
Such proportion could affect our analysis.


### Let's plot histograms and quartile box plot for all variables \
and would see their distributions



```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = residual.sugar ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = residual.sugar, fill =I('darkorange')  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = quality ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = quality, fill =I('darkorange')  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = volatile.acidity ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = volatile.acidity, fill =I('darkorange')  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = fixed.acidity ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = fixed.acidity, fill =I('darkorange') ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = chlorides ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = chlorides, fill =I('darkorange')  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = total.sulfur.dioxide ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = total.sulfur.dioxide, fill =I('darkorange') ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = pH ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = pH , fill =I('darkorange')) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = citric.acid ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = citric.acid , fill =I('darkorange') ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = free.sulfur.dioxide ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = free.sulfur.dioxide, fill =I('darkorange')  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}

grid.arrange(ggplot(redWine, aes( x = 1, y = sulphates ) ) + 
               geom_jitter(alpha = 0.1 ) +
               geom_boxplot(alpha = 0.2, color = 'red' ) ,
             ggplot(redWine, aes( x   = sulphates, fill =I('darkorange')  ) ) + 
                   geom_histogram(bins=30 ),ncol=2)
```


- many variables are normally distributed:
  - quality
  - volatile acidity
  - pH
  - chlorides (or it's only has this value)
- Alcohol and Fixed Acidity, Total Sulfur Dioxide, Citric Acid, Free Sulfur dioxide, sulphates are right skewed
- As noticed above we have mostly 'Good' wine samples


As we see:
- for alcohol, chlorides and sulphates most of data lays in middle 50%.
- residual sugar has many values in last quartile
- citric Acid and pH have values in all quartiles
- free sulfur dioxide has mostly values in upper 75%.


### Creating Histogram with log scale for Right skewed variables

```{r echo=FALSE, message=FALSE, warning=FALSE}

pALog <- qplot(x=alcohol, data=redWine, fill =I('darkorange'))+
  scale_x_log10()

pRSLog <- qplot(x=residual.sugar, data=redWine, fill =I('darkorange'))+
  scale_x_log10()

pSFLog <- qplot(x=free.sulfur.dioxide, data=redWine, fill =I('darkorange'))+
  scale_x_log10()

pCALog <- qplot(x=citric.acid, data=redWine, fill =I('darkorange'))+
  scale_x_log10()

grid.arrange(pALog, pRSLog, pSFLog, pCALog)
```


As we see even after applying log10  'alcohol' and 'residual sugar' \
distributions are still right skewed, 'free sulfur dioxide' became almost \
normally skewed and 'Citric acid' became left skewed.


### Let's check how different variables represented in Quality groups

#### Alcohol in Quality Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
pA <- ggplot(redWine, aes(x = alcohol, fill = QualityGroup)) +
  geom_histogram(position = "dodge", binwidth = 1)
pA + scale_fill_brewer(palette = 'Oranges')
```

Most 'Good' wines hav Alcohol level between 9 and 12.5.

#### Residual sugar in Quality Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
pRS <- ggplot(redWine, aes(x = residual.sugar, fill = QualityGroup)) +
  geom_histogram(position = "dodge", binwidth = 1)
pRS + scale_fill_brewer(palette = 'Oranges')
```

'Good' wines have Residual sugar between 2.5 and 4.5.

#### Citric Acid in Quality Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
pCA <- ggplot(redWine, aes(x = citric.acid, fill = QualityGroup)) +
  geom_histogram(position = "dodge", binwidth = .2)
pCA + scale_fill_brewer(palette = 'Oranges')
```


'Good' Wines have Citric acis between 0.1 an 0.7.

#### Free sulfur dioxide in Quality Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
pFS <- ggplot(redWine, aes(x = free.sulfur.dioxide, fill = QualityGroup)) +
  geom_histogram(position = "dodge", binwidth = 5)
pFS + scale_fill_brewer(palette = 'Oranges')
```


'Good' wines have Free sulfur dioxide from 5 to 40.

# Univariate Analysis


### What is the structure of your dataset?
- 1599 red wine samples
- 11 variables + 1 created Quality Group.

```{r, echo=FALSE, message=FALSE, warning=FALSE, names}
names(redWine)
```


### What is/are the main feature(s) of interest in your dataset?

- Quality of the red wine. 
I'm analyzing data to understand if it's possible to predict quality of \
the wine based on values of given variables.


### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
- Alcohol factor,
- Citric Acid factor,
- Residual Sugar facror,
- Free Sulfur dioxide factor,
I'm analyzing these factors to check how they affect Quality of the wine.


### Did you create any new variables from existing variables in the dataset?

Yes, I've created Quality Group  variable, grouping existing quality ranking: 
As we seen from the plots and summary we don't have wine with ranking 1,2 \
(which is supposed to be 'very bad' and 9,10 which is supposed to be \
'very excellent').

I've groupped the rest into groups:
"Bad": ranking 3,4
"Good" ranking 5,6
"Excellent": ranking 7,8

As we see, the most of the samplses 85% falls into 'Good' wine category.
Such proportion could affect our analysis.



### Of the features you investigated, were there any unusual distributions? \

Alcohol, Residual sugar, Free sulfur dioxide and Fixed Acidity have right \
skewed distribution.
After applying log10  'alcohol' and 'residual sugar' \
distributions are still right skewed, 'free sulfur dioxide' became almost \
normally skewed and 'Citric acid' became left skewed.


# Bivariate Plots Section

### Plot Quality groups and variables

```{r echo=FALSE, message=FALSE, warning=FALSE}

qA <- ggplot(redWine, aes(x= QualityGroup, y = alcohol)) + geom_point()
qH <- ggplot(redWine, aes(x= QualityGroup, y = pH)) + geom_point()
qRS <- ggplot(redWine, aes(x= QualityGroup, y = residual.sugar)) + geom_point()
qFA <- ggplot(redWine, aes(x= QualityGroup, y = fixed.acidity)) + geom_point()
qT <- ggplot(redWine, aes(x= QualityGroup, y = total.sulfur.dioxide)) + geom_point()
qVA <- ggplot(redWine, aes(x= QualityGroup, y = volatile.acidity)) + geom_point()

grid.arrange(qA, qH, qRS, qFA, qT, qVA)
```


These plots allow us to see level of each variables for each Quality group.



### Creating correlation matrix to see the correlation between variables

```{r echo=FALSE, message=FALSE, warning=FALSE}

#https://www.statmethods.net/stats/correlations.html

# in order to use cor function need to have all numerical data

corWine <- round(cor(redWine[2:13][sapply(redWine[13], is.numeric)]),2)
corWine
```

### Crealtion correlation plots to visualize the correlation

```{r echo=FALSE, message=FALSE, warning=FALSE, Correlation_Plots}

#http://www.sthda.com/english/wiki/elegant-correlation-table-using-xtable-r-package

corWine2 <- rcorr(as.matrix(redWine[2:13][sapply(redWine[13], is.numeric)]))
corWine2

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

corrplot(corWine, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
corrplot.mixed(corWine)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
corrplot(corWine,  method = "ellipse")

```


As we see from plots and the table the strongest correlation we have between:
 - Quality and alcohol
 - Quality and volatile acidity
 - Alcohol and Citric Acid
 - Alcohol and Density
 - Alcohol and pH
 - Citric Acid and Fixed Acidity
 - Citric Acid and pH
 
```{r echo=FALSE, message=FALSE, warning=FALSE}

heatmap(x = corWine, col = col, symm = TRUE)
```

# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \

As we see from plots and the table the strongest correlation we have between:
 - Quality and alcohol
 - Quality and volatile acidity
 - Alcohol and Citric Acid
 - Alcohol and Density
 - Alcohol and pH
 - Citric Acid and Fixed Acidity
 - Citric Acid and pH

We see that Quality is mostly correlated to Alcohol content and Volatile \
Acidity. 
Citric Acid is strongly correlated with Volatile Acidity and Fixed \
Acidity.
Density is strongly correlated with ph, Alcohol, Acidity.

I belive that limitation of dataset (most of wines from medium 'Good' quality \
wines are affecting found relationship)


### What was the strongest relationship you found?

The strongest relationship s between pH and fixed acidity which totally makes \
sense from chemical point of view.
The rest strongest are between differen acitiy variables, and than between \
sulfur variables.


# Multivariate Plots Section



```{r echo=FALSE, message=FALSE, warning=FALSE}
#https://ggplot2.tidyverse.org/reference/scale_brewer.html
ggplot(aes(factor(QualityGroup), 
            alcohol), 
        data = redWine) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
dpHA <- ggplot(data=redWine, aes(x=pH, y=alcohol ,color=QualityGroup))+
  geom_point()+
  geom_smooth(method='lm', se=FALSE)
dpHA
```


'Excellent' wines tend to have higher alcohol and lower pH level.

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(aes(factor(QualityGroup), 
            citric.acid), 
        data = redWine) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

dCAA <- ggplot(data=redWine, aes(x=citric.acid, y=alcohol ,color=QualityGroup))+
  geom_point()+
  geom_smooth(method='lm', se=FALSE)
dCAA
```


Most of 'Good' wines have lower alcohol content and acidity than 'Excellent' \
ones.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(factor(QualityGroup), 
            density), 
        data = redWine) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
dDAA <- ggplot(data=redWine, aes(x=density, y=alcohol ,color=QualityGroup))+
  geom_point()+
  geom_smooth(method='lm', se=FALSE)
dDAA
```


As we see higher alcohol content correlates with lower density.


```{r echo=FALSE, message=FALSE, warning=FALSE}
smoothDA <- ggplot(data = redWine,
       aes(y = density, x = (alcohol),
           color = factor(quality))) +
  geom_point(alpha = 0.5, size = 1) +
  geom_smooth(method = "lm", se = FALSE,size=1)  +
  scale_color_brewer(type='seq', palette = "Greens",
                   guide=guide_legend(title='Quality'))
smoothDA
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
smoothRSA <- ggplot(data = redWine,
       aes(y = residual.sugar, x = (alcohol),
           color = factor(QualityGroup))) +
  geom_point(alpha = 0.8, size = 1) +
  geom_smooth(method = "lm", se = FALSE,size=1)  +
  scale_y_continuous(limits=c(1,10)) +
  facet_wrap(~QualityGroup) +
  scale_color_brewer(type='seq', palette = "Blues",
                   guide=guide_legend(title='Quality'))
smoothRSA
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
smoothSA <- ggplot(data = redWine,
       aes(y = sulphates, x = (alcohol),
           color = factor(quality))) +
  geom_point(alpha = 0.8, size = 1) +
  geom_smooth(method = "lm", se = FALSE,size=1)  +
  scale_y_continuous(limits=c(0.4,1.4)) +
  facet_wrap(~QualityGroup) +
  scale_color_brewer(type='seq', palette = "Greens",
                   guide=guide_legend(title='Quality'))
smoothSA

```


As we see in 'Excellent' wine group samples thend to have higher alcohol cotent,
lower residual sugar and average leve of sulphates.
The higher alcohol content of the 'Excellent' wine the lower the density.
To my knowledge, sulphates are added to wine as preservatives and lack of them \
would lead to unpleasant taste.

# Multivariate Analysis

### Creating linear model
```{r echo=FALSE, message=FALSE, warning=FALSE, linear_model}

#https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_mixed.html
m1 <- lm(as.numeric(quality) ~ alcohol, data = redWine)
m2 <- update(m1, ~ . + density)
m3 <- update(m2, ~ . + citric.acid)
m4 <- update(m3, ~ . + volatile.acidity)
m5 <- update(m4, ~ . + density)
#m6 <- update(m5, ~ . + fixed.acidity)
#m7 <- update(m6, ~ . + pH)
mtable(m1,m2,m3,m4,m5)
```

The variables in this linear model can account for 32% of the variance \
in the quality of red wine. R-squared of 0.32, so the data is only moderate \
at fitting the regression model though it has increased from 0.22.


### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

As alcohol is strongly correlated to wine Quality ranking I've checked factors \
which correlates to alcohol.
I see that Alcohol and Density are negatively correlated as well as \
Alcohol and Residual Sugar.



### Were there any interesting or surprising interactions between features?

Almost none. The basic chemical knowledge explains the relationship between pH \
and acidity levels.
Given that too tart or sour wine don't have very pleasant taste high quality \
wines usually have moderate level of acidity.

### OPTIONAL: Did you create any models with your dataset? 

I've created a linear model.

With linear model it's become clear that The variables in this linear model \
can account for 32% of the variance in the quality of red wine. \
R-squared of 0.32, so the data is only moderate \
at fitting the regression model though it has increased from 0.22.


------

# Final Plots and Summary


### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_one}

corrplot(corWine, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, title = "Correlation Matrix", 
         mar=c(0,0,1,0)) 
```

### Description One
The Correlation Matrix allows us to see main relationship between variables.
The stongest correlations are beteen:
 - Quality and alcohol
 - Quality and volatile acidity
 - Alcohol and Citric Acid
 - Alcohol and Density
 - Alcohol and pH
 - Citric Acid and Fixed Acidity
 - Citric Acid and pH

We see that Quality is mostly correlated to Alcohol content and Volatile \
Acidity. 
Citric Acid is strongly correlated with Volatile Acidity and Fixed \
Acidity.
Density is strongly correlated with ph, Alcohol, Acidity.

### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}
dDA2 <- ggplot(data=redWine, aes(x=density, y=alcohol ,color=QualityGroup))+
  geom_point()+
  geom_smooth(method='lm', se=FALSE)+
  ggtitle('Alcohol and Density for differen wine Quality groups') +
  ylab('Alcohol content, %') +
  xlab('Density')
dDA2
```

### Description Two

As we see higher Quality correlates to higher alcohol content \
and lower density.

### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}
ggplot(aes(factor(QualityGroup), 
            citric.acid), 
        data = redWine) +
  geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue')+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4) +
  ggtitle('Citric Acid for different wine Quality groups') +
  ylab('Citric Acid') +
  xlab('Quality Groups')

```

### Description Three

'Excellent' wines have higher alcohol content and medium level of acidity,

------

# Reflection

As seen from initial Quality ranking in this dataset we don't have neither \
'very bad' not 'very excellent' wines. So we can't see what qualities and \
characteristics are typical for exceptional (both ways) wines.

Most of our samples come from average 'Good' wines which limits our abitily \
to make correct predicitions about quality.

I found that:
- Alcohol is very important factor in Quality group. Most 'Excellent' wines \
have 11%-12% content (minimum alcohol content in our samples is 8.4%)
- Alcohol and density are negatively correlated which is due to chemistry.
- Sulphates and sulfites are added to wine to preserve taste, so it's 
unlikely to find decent wine without these ingredients.
- The acidity is very important factor but it has to be balanced to avoid \
tart or too sweet taste.

This analysis is highly liited by uneven quality distribution and as \
linea model shows, provided factors only explaine 32% of quality variance.

I've checked few resourses about wine to get some guidance about wine quality \
and tasting and found interesting information which confirmes my \
analysis:

###The additionsl information: 

**WIKI**:
In wine tasting, humans are least sensitive to the taste of sweetness \ 
(in contrast to sensitivity to bitterness or sourness) with the majority of the \
population being able to detect sugar or "sweetness" in wines between 1% and \
2.5% residual sugar. Additionally, other components of wine such as acidity and \
tannins can mask the perception of sugar in the wine.
https://en.wikipedia.org/wiki/Sugars_in_wine#In_wine_tasting

The acidity in wine is an important component in the quality and taste \
of the wine. It adds a sharpness to the flavors and is detected most readily \
by a prickling sensation on the sides of the tongue and a mouth-watering \
aftertaste. Of particular importance is the balance of acidity versus the 
sweetness of the wine (the leftover residual sugar) and the more bitter \
components of the wine (most notably tannins but also includes other \
phenolics). A wine with too much acidity will taste excessively sour and sharp.\
A wine with too little acidity will taste flabby and flat, with less defined \
flavors.
https://en.wikipedia.org/wiki/Acids_in_wine#In_wine_tasting


High alcohol levels come from a high amount of sugar in the fermentation \
process, which the yeast converts into ethanol.
https://vincarta.com/blog/choose-best-red-wine/
